### 2015-04-01 cug_paper/02_design.tex
Paper: Adding figures
Added great big figure showing the communications steps

\subsection{Overview}
\label{subsec:overview}
This idea was tested using a synthetic benchmark application written by the authors.  The benchmark consists of two executables: the main executable which simulates the I/O patterns of a typical HPC application and a daemon process that is started on each compute node.  The daemon has two tasks: manage the GPU memory and copy data from GPU memory out to a file.  Note that the daemon does \emph{not} copy the data into the GPU memory.  There needs to be exactly one daemon process on each compute node regardless of how many MPI ranks are running on each node.  \footnote{Due to the limitations of aprun, starting this daemon is somewhat involved.  See section \ref{subsec:cray-specific}.}

With the daemon \todo{Should 'daemon' be plural?} started, the application begins its main execution.  In this case, since it's just a synthetic 
I/O benchmark, it performs no actual computation; it simply writes a specified amount of data and then sleeps for a specified amount of time.  For these tests, the sleep time was deliberately calculated to allow enough time for the data in GPU memory to drain.

>>>>

\todo[inline]{Somewhere in here, we're going to want to insert the graph of host-to-gpu bandwidth vs. transfer size.  It justifies chosing 16MB bocks and we're going to want to reference it from the analysis section, too.}

\subsection{Overview}
\label{subsec:overview}
This idea was tested using a synthetic benchmark application written by the authors.  The benchmark consists of two executables: the main executable which uses MPI and simulates the I/O patterns of a typical HPC application and a daemon process that is started on each compute node.  The daemon has two tasks: manage the GPU memory and copy data from GPU memory out to a file.  Note that the daemon does \emph{not} copy the data into the GPU memory.  There needs to be exactly one daemon process on each compute node regardless of how many MPI ranks are running on each node.  \footnote{Due to the limitations of aprun, starting this daemon is somewhat involved.  See section \ref{subsec:cray-specific}.}

With the daemon process running on each node, the application begins its main execution.  In this case, since it's just a synthetic 
I/O benchmark, it performs no actual computation; it simply writes a specified amount of data and then sleeps for a specified amount of time.  For these tests, the sleep time was deliberately calculated to allow enough time for the data in GPU memory to drain.

\begin{figure*}[!t]
\centerline{
  \subfloat[Application sends write request message to daemon]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide09}%
    \label{fig:comm_a}}
  \hfil
  \subfloat[Daemon allocates GPU memory and converts pointer into IPC handle]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide10}%
    \label{fig:comm_b}}}
\centerline{
  \subfloat[Daemon sends reply message with IPC handle]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide11}%
    \label{fig:comm_c}}
  \hfil
  \subfloat[Application writes data to GPU memory]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide12}%
    \label{fig:comm_d}}}    
\centerline{
  \subfloat[Application sends write complete message to daemon]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide13}%
    \label{fig:comm_e}}
  \hfil
  \subfloat[Daemon copies data from GPU memory to system memory]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide14}%
    \label{fig:comm_f}}} 
\centerline{
  \subfloat[Daemon writes data to filesystem]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide15}%
    \label{fig:comm_g}}} 
\caption{Communications steps}
\label{fig_sim}
\end{figure*}
